---
title: Powerplay
subtitle: Data Cleaning and Wrangling
---

## Ball-by-ball data

There are total 22 columns in the raw ball-by-ball data. They are following:

```{r, message=FALSE, warning=FALSE}
#| echo: false
library(tidyverse)
t20 <- readRDS(file = "./data/t20_raw_data09JAN2025_1219.rds")
```

```{r}
glimpse(t20)
```

**Next we will perform the data cleaning steps as below.**

-   Replacing all `NA` values with 0.

```{r, eval=FALSE}
t20[t20 == ""] <- NA
t20[is.na(t20)] <- 0
```

-   Removing `season`, `other_wicket_type` and `other_player_dismissed` column as they are not required in our analysis.

-   Creating a new variable `over` i.e. the over number at which the particular ball was bowled and `over_type` i.e. the phase of play (Powerplay, Middle Over, Death Over).

-   Next, creating bunch of binary variables `isOne`, `isTwo`, `isThree`, `isFour`, `isSix` from `runs_off_bat` and `isOut` from `wicket_type`. Also, creating another variable `team_runs` after combining `runs_off_bat` and `extras`.
